### 2017-08-23 natural-deduction.tex
error in compilation

\subsection{Categorical Interpretation of Natural Deductions}

$T$ rules: in the symmetric monoidal closed category of the adjunction model

T\_identity: $id_X:X\rightarrow X$

T\_unitI:

T\_unitE: given $t_1:\Delta\rightarrow Unit$ and $t_2:\Gamma\rightarrow Y$, returns
$\lambda_Y\circ(t_1\otimes t_2):\Gamma\otimes\Delta\rightarrow Unit\otimes Y\rightarrow Y$

T\_tenI: given $t_1:\Gamma\rightarrow X$ and $t_2:\Delta\rightarrow Y$, returns
$t_1\otimes t_2:\Gamma\otimes\Delta\rightarrow X\otimes Y$

T\_tenE: given $t_1:\Gamma\rightarrow X\otimes Y$ and
$t_2:\Delta\otimes X\otimes Y\rightarrow Z$, returns \\
$t_2\circ\e{X\otimes Y,\Delta}\circ t_1\otimes id_\Delta:\Gamma\otimes\Delta\rightarrow(X\otimes Y)\otimes\Delta\rightarrow\Delta\otimes(X\otimes Y)\rightarrow Z$

T\_implI:

T\_implE:

T\_imprI:

T\_imprE:

T\_GI: given $s:FX_1\otimes'...\otimes' FX_n\rightarrow A$, returns \\
$Gs\circ G\m{}^{-1}\circ\eta:X_1\otimes...\otimes X_n\rightarrow GF(X_1\otimes...\otimes X_n)\rightarrow G(FX_1\otimes'...\otimes'FX_n)\rightarrow GA$

S rules: in the Lambek category of the adjunction model

S\_identity: $id_A:A\rightarrow A$

S\_unitI:

S\_unitE:

\subsection{Normaalization and Reduction}

>>>>

The term assignment for natural deduction of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-nd-smcc}. And the term assignme for the
non-commutative part, i.e. the Lambek category of the adjunction, is defined in
Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the non-commutative part
and they are lists. $[[G]]$ and $[[D]]$ are contexts for the commutative part and they are
multisets, therefore the following exchange rules are implicit.
\scriptsize
\begin{mathpar}
  \ottdruleTXXbeta{} \qquad\qquad \ottdruleSXXbeta{}
\end{mathpar}

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \ottdruleTXXid{} \qquad\qquad \ottdruleTXXunitI{} \qquad\qquad \ottdruleTXXunitE{} \\
      \ottdruleTXXtenI{} \qquad\qquad \ottdruleTXXtenE{} \\
      \ottdruleTXXimpI{} \qquad\qquad \ottdruleTXXimpE{} \qquad\qquad \ottdruleTXXGI{}
    \end{mathpar}
  \end{mdframed}
\caption{Commutative Part}
\label{fig:elle-nd-smcc}
\end{figure}

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \ottdruleSXXid{} \qquad\qquad \ottdruleSXXunitI{} \qquad\qquad \ottdruleSXXunitEOne{} \\
      \ottdruleSXXunitETwo{} \qquad\qquad \ottdruleSXXunitEThree{} \\
      \ottdruleSXXunitEFour{} \qquad\qquad \ottdruleSXXtenI{} \\
      \ottdruleSXXtenEOne{} \qquad\qquad \ottdruleSXXtenETwo{} \\
      \ottdruleSXXimprI{} \qquad\qquad \ottdruleSXXimprE{} \qquad\qquad \ottdruleSXXimplI{} \\
      \ottdruleSXXimplE{} \qquad\qquad \ottdruleSXXFI{} \\
      \ottdruleSXXFE{} \qquad\qquad \ottdruleSXXGE{}
    \end{mathpar}
  \end{mdframed}
\caption{Non-Commutative Part}
\label{fig:elle-nd-lambek}
\end{figure}

\begin{center}
  \tiny
  \begin{math}
  $$\mprset{flushleft}
  \inferrule* [right={\tiny imprI}] {
    $$\mprset{flushleft}
    \inferrule* [right={\tiny tenE2}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny id}] {
        \,
      }{[[z : h(F Gf A) (>) F Gf B |-l z : h(F Gf A) (>) F Gf B]]}
        $$\mprset{flushleft}
        \inferrule* [right={\tiny FE}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny id}] {
            \,
          }{[[x2 : F Gf A |-l x2 : F Gf A]]}
            $$\mprset{flushleft}
            \inferrule* [right={\tiny FE}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny id}] {
                \,
              }{[[y2 : F Gf B |-l y2 : F Gf B]]}
              \inferrule* [right={\tiny beta}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny FE}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny FI}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny id}] {
                      \,
                    }{[[y0 : Gf B |-c y0 : Gf B]]}
                  }{[[y0 : Gf B |-l F y0 : F Gf B]]}
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny FI}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny id}] {
                      \,
                    }{[[x0 : Gf A |-c x0 : Gf A]]}
                  }{[[x0 : Gf A |-l F x0 : F Gf A]]}
                }{[[y0 : Gf B, x0 : Gf A |-l h(F y0) (>) F x0 : h(F Gf B) (>) F Gf A]]}
              }{[[x1 : Gf A, y1 : Gf B |-l ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0) : h(F Gf B) (>) F Gf A]]}
            }{[[x1 : Gf A , y2 : F Gf B |-l let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)) : h(F Gf B) (>) F Gf A]]}
          }{[[x2 : F Gf A , y2 : F Gf B |-l let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0))) : h(F Gf B) (>) F Gf A]]}
        }{[[z : h(F Gf A) (>) F Gf B |-l let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : h(F Gf B) (>) F Gf A]]}
      }{[[ . |-l \r z : h(F Gf A) (>) F Gf B.let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : (h(F Gf A) (>) F Gf B) -> (h(F Gf B) (>) F Gf A)]]}
  \end{math}
\end{center}

### 2017-08-23 sequent-calculus.tex
error in compilation

The term assignment for natural deduction of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-nd-smcc}. And the term assignme for the
non-commutative part, i.e. the Lambek category of the adjunction, is defined in
Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the non-commutative part
and they are lists. $[[G]]$ and $[[D]]$ are contexts for the commutative part and they are
multisets, therefore the following exchange rules are implicit.
\scriptsize
\begin{mathpar}
  \ottdruleTXXbeta{} \qquad\qquad \ottdruleSXXbeta{}
\end{mathpar}

@@

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \ottdruleSXXid{} \qquad\qquad \ottdruleSXXunitI{} \qquad\qquad \ottdruleSXXunitEOne{} \\
      \ottdruleSXXunitETwo{} \qquad\qquad \ottdruleSXXunitEThree{} \\
      \ottdruleSXXunitEFour{} \qquad\qquad \ottdruleSXXtenI{} \\
      \ottdruleSXXtenEOne{} \qquad\qquad \ottdruleSXXtenETwo{} \\
      \ottdruleSXXimprI{} \qquad\qquad \ottdruleSXXimprE{} \qquad\qquad \ottdruleSXXimplI{} \\
      \ottdruleSXXimplE{} \qquad\qquad \ottdruleSXXFI{} \\
      \ottdruleSXXFE{} \qquad\qquad \ottdruleSXXGE{}
    \end{mathpar}
  \end{mdframed}
\caption{Non-Commutative Part}
\label{fig:elle-nd-lambek}
\end{figure}

\begin{center}
  \tiny
  \begin{math}
  $$\mprset{flushleft}
  \inferrule* [right={\tiny imprI}] {
    $$\mprset{flushleft}
    \inferrule* [right={\tiny tenE2}] {
      $$\mprset{flushleft}
      \inferrule* [right={\tiny id}] {
        \,
      }{[[z : h(F Gf A) (>) F Gf B |-l z : h(F Gf A) (>) F Gf B]]}
        $$\mprset{flushleft}
        \inferrule* [right={\tiny FE}] {
          $$\mprset{flushleft}
          \inferrule* [right={\tiny id}] {
            \,
          }{[[x2 : F Gf A |-l x2 : F Gf A]]}
            $$\mprset{flushleft}
            \inferrule* [right={\tiny FE}] {
              $$\mprset{flushleft}
              \inferrule* [right={\tiny id}] {
                \,
              }{[[y2 : F Gf B |-l y2 : F Gf B]]}
              \inferrule* [right={\tiny beta}] {
                $$\mprset{flushleft}
                \inferrule* [right={\tiny FE}] {
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny FI}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny id}] {
                      \,
                    }{[[y0 : Gf B |-c y0 : Gf B]]}
                  }{[[y0 : Gf B |-l F y0 : F Gf B]]}
                  $$\mprset{flushleft}
                  \inferrule* [right={\tiny FI}] {
                    $$\mprset{flushleft}
                    \inferrule* [right={\tiny id}] {
                      \,
                    }{[[x0 : Gf A |-c x0 : Gf A]]}
                  }{[[x0 : Gf A |-l F x0 : F Gf A]]}
                }{[[y0 : Gf B, x0 : Gf A |-l h(F y0) (>) F x0 : h(F Gf B) (>) F Gf A]]}
              }{[[x1 : Gf A, y1 : Gf B |-l ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0) : h(F Gf B) (>) F Gf A]]}
            }{[[x1 : Gf A , y2 : F Gf B |-l let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)) : h(F Gf B) (>) F Gf A]]}
          }{[[x2 : F Gf A , y2 : F Gf B |-l let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0))) : h(F Gf B) (>) F Gf A]]}
        }{[[z : h(F Gf A) (>) F Gf B |-l let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : h(F Gf B) (>) F Gf A]]}
      }{[[ . |-l \r z : h(F Gf A) (>) F Gf B.let z : h(F Gf A) (>) F Gf B be x2 (>) y2 in (let F x1 : F Gf A be x2 in (let F y1 : F Gf B be y2 in (ex y1 , x1 with y0 , x0 in (h(F y0) (>) F x0)))) : (h(F Gf A) (>) F Gf B) -> (h(F Gf B) (>) F Gf A)]]}
  \end{math}
\end{center}

>>>>

The term assignment for sequent calculus of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-smcc}.

@@
